Auditory Scene Similarity Retrieval and Classification with Relevance-based Quantization of Scattering Features

### 2016-12-16 paper/structureScene.tex
Change k to q for NN parameter

The similarity between the scene centroids $\mu_m^u$ over the entire dataset, is computed using a radial basis function (RBF) kernel $K$ combined with the local scaling method proposed in \cite{selfTuneManor2004}:
\begin{equation}
\label{eq:kc}
K_{mn}^{uv} = \exp\left( - \dfrac{\Vert \mu_m^u - \mu_n^v \Vert^2}{\Vert \mu_m^u - \mu_{m,k}^u \Vert \Vert \mu_n^v - \mu_{n,k}^v \Vert} \right).
\end{equation} 
Here, $\mu_{m,k}^u$ and $\mu_{n,k}^v$ are the $k^{\textrm{th}}$ nearest neighbors to the centroids $\mu_m^u$ and $\mu_n^v$, respectively, and $\Vert \cdot \Vert$ denotes the Euclidean norm.

@@

For ASSR, evaluation is performed on the private part of the DCASE 2013 dataset. The metric used is the precision at rank $k$ ($p@k$), which is computed by taking a query item and counting the number of items of the same class within the $k$ closest neighbors, and then averaging over all query items. \ja{The variable $k$ is used previously, so we should change that.} The $p@k$ is computed for $k=\lbrace 1,\ldots,9\rbrace$, since each class only has $10$ items. Note that a $p@1$ is equivalent to the classification accuracy obtained by the classifier which chooses the label of the closest neighbor for a given item. For each experimental setting, we only report the results obtained with the sets of parameters, \emph{i.e.} the number of clusters $M$ for the \emph{ob} approaches and the scaling parameter $k$ of the RBF kernels (see Eq. \ref{eq:kc}) leading to the best $p@9$. The \emph{ob} approaches are compared to commonly used early integration approach \emph{early}.

>>>>

The similarity between the scene centroids $\mu_m^u$ over the entire dataset, is computed using a radial basis function (RBF) kernel $K$ combined with the local scaling method proposed in \cite{selfTuneManor2004}:
\begin{equation}
\label{eq:kc}
K_{mn}^{uv} = \exp\left( - \dfrac{\Vert \mu_m^u - \mu_n^v \Vert^2}{\Vert \mu_m^u - \mu_{m,q}^u \Vert \Vert \mu_n^v - \mu_{n,q}^v \Vert} \right).
\end{equation} 
Here, $\mu_{m,q}^u$ and $\mu_{n,q}^v$ are the $q^{\textrm{th}}$ nearest neighbors to the centroids $\mu_m^u$ and $\mu_n^v$, respectively, and $\Vert \cdot \Vert$ denotes the Euclidean norm.

@@

For ASSR, evaluation is performed on the private part of the DCASE 2013 dataset. The metric used is the precision at rank $k$ ($p@k$), which is computed by taking a query item and counting the number of items of the same class within the $k$ closest neighbors, and then averaging over all query items. The $p@k$ is computed for $k=\lbrace 1,\ldots,9\rbrace$, since each class only has $10$ items. Note that a $p@1$ is equivalent to the classification accuracy obtained by the classifier which chooses the label of the closest neighbor for a given item. For each experimental setting, we only report the results obtained with the sets of parameters, \emph{i.e.} the number of clusters $M$ for the \emph{ob} approaches and the scaling parameter $q$ of the RBF kernels (see Eq. \ref{eq:kc}) leading to the best $p@9$. The \emph{ob} approaches are compared to commonly used early integration approach \emph{early}.
